---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rstudioTeachMode

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/rstudioTeachMode)](https://CRAN.R-project.org/package=rstudioTeachMode)
[![Codecov test coverage](https://codecov.io/gh/murraycadzow/rstudioTeachMode/branch/master/graph/badge.svg)](https://codecov.io/gh/murraycadzow/rstudioTeachMode?branch=master)
[![R build status](https://github.com/murraycadzow/rstudioTeachMode/workflows/R-CMD-check/badge.svg)](https://github.com/murraycadzow/rstudioTeachMode/actions)
<!-- badges: end -->

The goal of rstudioTeachMode is to provide an easy mechanism to switch between theme preferences for personal use and theme preferences for a teaching environment.

## Installation

This package is under development and very experimental but can be installed from github using

``` r
remotes::install_github("murraycadzow/rstudioTeachMode")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(rstudioTeachMode)
## basic example code
```

